\section*{Experience}
\begin{itemize}[leftmargin=*]
    \item \textbf{AI Research Intern, Copado} \\
    June - August 2024 \\
    Analyzed GPU memory consumption for multithreading with sentiment analysis classifier. Programmed AI model in Python for retrieval augmented generation (RAG) using vector similarity search with Neo4j.

    \item \textbf{Machine Learning Research Assistant, NYU Langone Health} \\
    November 2023 - May 2024 \\
    Collaborated with medical professionals to analyze pre and post-operative knee replacement data. Performed feature selection using Scikit-learn algorithms and communicated results to the research team.

    \item \textbf{Multiple Roles, Washington and Lee University}
    \begin{itemize}
        \item \textbf{Computer Vision Research, Dept. of Neuroscience} \\
        April - May 2024 \\
        Developed visual transformer model to classify images of ovarian structures in rats with 98\% accuracy.
        
        \item \textbf{Machine Learning Research Assistant, Dept. of Neuroscience} \\
        January - April 2023 \\
        Suggested ML algorithms for predictive modeling. Developed neural net classifier using PyTorch and NumPy with 96\% classification accuracy.
        
        \item \textbf{Data Mining Intern, Dept. of Data Science} \\
        June - September 2022 \\
        Collaborated on data collection and established a research base for digital estate management services.
        
        \item \textbf{Teaching Assistant, Dept. of Computer Science} \\
        September 2021 - April 2022 \\
        Advised students and organized office hours for courses in Python and Data Structures in C.
    \end{itemize}
\end{itemize}
